A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-20 writeup/paper.tex
table instead of pie chart

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/natlang-pie}
\caption{Self-reported native language of 3,154 bilingual turkers}
\label{lang-pie}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In order to address the quality of the translations we received on the dictionary task, we constructed a pipeline in which the output of the translation HIT was reviewed by humans in a second evaluation HIT, described above. We quantified the quality of each translation assignment based on the output of the evaluation HIT. The quality of an assignment was scored as the fraction of known words which were acceptably translated: i.e, the supplied translation was judged to be synonymous with the gold standard translation. Since each assignment had either one or two known words embedded, each assignment was assigned a score of either 0, 0.5, or 1.

%%%%%%%%%%%%%%% MISREPORT TABLE %%%%%%%%%%%
\begin{figure}[h]
\centering
\begin{tabular}{cccc}\hline\hline\\
&Avg. & 99\%&\\
&Quality & Conf. Int.&n\\
Misreport&0.252&(0.244, 0.260)&10,479\\
Correct&0.282&(0.280, 0.283)&296,911\\
Overall&0.281&(0.279, 0.282)&307,390\\
\hline\hline
\end{tabular}
\label{mism-tab}
\caption{Quality of translations recieved from truthful versus misreporting Turkers.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Self-reported country information is typically reliable. Three quarters of Turkers who reported their native language reported a single native language consistantly across all assignments (table \ref{numlangs-tab}), and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language, meaning less than 5\% of Turkers gave unreasonable responses. Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.

>>>>

%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
\begin{figure}[h]
\begin{tabular}{cc}\hline\hline
Language&\# Turkers\\
\hline
English&591\\
Tamil&253\\
Malayalam&219\\
Hindi&149\\
Spanish&131\\
Telugu&87\\
Chinese&86\\
Romanian&85\\
Portuguese&82\\
Arabic&74\\
Kannada&72\\
German&66\\
French&63\\
Polish&61\\
Urdu&56\\
Tagalog&54\\
Marathi&48\\
Russian&44\\
Italian&43\\
Bengali&41\\
Gujarati&39\\
Hebrew&38\\
Dutch&37\\
Turkish&35\\
Vietnamese&34\\
Macedonian&31\\
Cebuano&29\\
Swedish&26\\
Bulgarian&25\\
Hungarian&23\\
Swahili&23\\
Thai&22\\
Catalan&22\\
Lithuanian&21\\
Punjabi&21\\
Other($\leq$ 20 per language)&423\\
\hline\hline
\end{tabular}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
%\begin{figure*}[h]
%\centering
%\includegraphics[width=7in]{figures/natlang-pie}
%\caption{Self-reported native language of 3,154 bilingual turkers}
%\label{lang-pie}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In order to address the quality of the translations we received on the dictionary task, we constructed a pipeline in which the output of the translation HIT was reviewed by humans in a second evaluation HIT, described above. We quantified the quality of each translation assignment based on the output of the evaluation HIT. The quality of an assignment was scored as the fraction of known words which were acceptably translated: i.e, the supplied translation was judged to be synonymous with the gold standard translation. Since most assignments had two known words embedded, most assignments had scores of either 0, 0.5, or 1.

%%%%%%%%%%%%%%% MISREPORT TABLE %%%%%%%%%%%
%\begin{figure}[h]
%\centering
%\begin{tabular}{cccc}\hline\hline\\
%&Avg. & 99\%&\\
%&Quality & Conf. Int.&n\\
%Misreport&0.252&(0.244, 0.260)&10,479\\
%Correct&0.282&(0.280, 0.283)&296,911\\
%Overall&0.281&(0.279, 0.282)&307,390\\
%\hline\hline
%\end{tabular}
%\label{mism-tab}
%\caption{Quality of translations recieved from truthful versus misreporting Turkers.}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Self-reported country information is typically reliable; about 96\% of self-reported locations agreed with automatically reported locations, 
Three quarters of Turkers who reported their native language reported a single native language consistantly across all assignments (table \ref{numlangs-tab}), and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language, meaning less than 5\% of Turkers gave unreasonable responses.

%Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.
